Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-12-11 ms.qmd
Cool ref and some more notes for writing

### ***Ecological consequences of reduced variation in physiological Rates***
The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remains unclear. The dearth of empirical data demonstrating changes in variance paired with a lack of theoretical models 
- buckley 2014, - Lawton 1991, - Nisbet

>>>>

### ***Ecological consequences of reduced variation in physiological Rates***
The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remains unclear. The dearth of empirical data demonstrating changes in variance paired with a lack of theoretical models 
- buckley 2014, - Lawton 1991, - Nisbet 
especailly see @kooijman1989population given that they "introduce some small spread" and it results in oscillatinos dapeming..
